Meta-analysis

### 2020-05-22 02_Preliminary_analysis.Rmd
Spell check all files
Clean up visualsation to use USQ colours and clean up code, etc.

```{r Fungicide_x_nSprays_tble2, message=FALSE}
PM_MB_means %>%
   group_by(fungicide_ai, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   footnote(general = "Fungicides with less than five observations were omitted from this table")

@@

PM_MB_means %>%
   mutate(fungicide_ai = as.factor(PM_MB_means$fungicide_ai)) %>%
   filter(total_fungicide == 1 | total_fungicide == 2) %>%
   filter(
      fungicide_ai != "pyrazophos" &
         fungicide_ai != "control" &
         fungicide_ai != "benomyl" &
         fungicide_ai != "Acibenzolar-S-methyl"
   ) %>%
   mutate(fungicide_ai = factor(
      fungicide_ai,
      levels = c(
         "carbendazim",
         "pyraclostrobin",
         "sulphur",
         "200 g/L azoxystrobin +\n80 g/L cyproconazole",
         "tebuconazole",
         "propiconazole",
         "200 g/L tebuconazole +\n120 g/L azoxystrobin"
      )
   )) %>%
   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
   facet_grid(rows = vars(total_fungicide)) +
   geom_boxplot(aes(fill = fungicide_ai, alpha = 0.5)) +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   labs(y = "Proportion of grain yield saved",
        title = "Grain yield proportion saved\ngrouped by fungicide type") +
   theme(legend.position = "none") +
   coord_flip()
```

@@

#### Fungicide Doses  
We should check that all fungicide doses that were used were roughly the same if we are to compare between trials were dose might be different.

```{r tebuAndPropi_dose}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   select(
      trial_ref,
      year,
      location,
      first_sign_disease,
      fungicide_ai,
      dose_ai.ha,
      total_fungicide
   ) %>%
   ggplot(aes(x = as.factor(dose_ai.ha), fill = fungicide_ai)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Total number of treatments for each respective tebuconazole dose") +
   geom_bar() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

@@

```{r PropiDoseEffect}
PM_MB_means %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = prop_YG)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Yield for each respective propiconazole dose") +
   geom_boxplot() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

@@

```{r spray_relative2FS}
PM_MB_means %>%
   mutate(
      s1_DfromFS = fungicide_application_1 - first_sign_disease,
      s2_DfromFS = fungicide_application_2 - first_sign_disease,
      s3_DfromFS = fungicide_application_3 - first_sign_disease,
      s4_DfromFS = fungicide_application_4 - first_sign_disease,
      s5_DfromFS = fungicide_application_5 - first_sign_disease
   ) %>%
   gather(
      key = spray,
      value = n_days,
      s1_DfromFS,
      s2_DfromFS,
      s3_DfromFS,
      s4_DfromFS,
      s5_DfromFS
   ) %>%
   drop_na(n_days) %>% 
   ggplot(aes(x = spray, y = as.numeric(n_days))) +
   geom_violin() +
   scale_x_discrete(
      labels = c(
         "First\nspray",
         "Second\nspray",
         "Third\nspray",
         "Fourth\nspray",
         "Fifth\nspray"
      )
   ) +
   ylab("Days to First Sign of Disease") +
   theme_usq()
```

@@

```{r Host_genotype}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(host_genotype, fungicide_ai, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   ggplot(aes(x = host_genotype, y = Treatments, fill = fungicide_ai)) +
   xlab("Cultivar") +
   ylab("N Trials") +
   ggtitle(label = "Cultivars used in either tebuconazole or propiconazole trials") +
   geom_col() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

&nbsp;

@@

YV1 <-
   yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
YV1[[2]]
YV1[[3]]
```
Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray treatments.
```{r yieldVol_control}

YV2 <-
   yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
YV2[[2]]
YV2[[3]]
```

Volatility of the cultivars are fairly similar when trial is not considered as a factor (when we inspect plots of all treatments and only spray treatments). Green Diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.

@@

Let's examine the same plots as above but only for the most commonly used trial site, Hermitage.  
```{r yieldVol_Herm}
YV1_herm <-
   yield_volatility(
      genotype_by_trial = FALSE,
      control_only = FALSE,
      location = "Hermitage"
   )
YV1_herm[[2]]
```

@@

Let's take a closer look at Crystal with spray management treatments and without.  
```{r YieldVol_Crystal}
YV1_crystal <-
   yield_volatility(genotype = "Crystal", control_only = FALSE)
YV1_crystal[[2]]
YV1_crystal <-
   yield_volatility(genotype = "Crystal", control_only = TRUE)
YV1_crystal[[2]]
```

@@

Let's look at Jade, to see if it differs.
```{r YieldVol_Jade}
YV2_crystal <- yield_volatility("Jade",control_only = FALSE)
YV2_crystal[[2]]
```

@@

```{r YieldVol_JadeControl}
YV3_crystal <- yield_volatility("Jade", control_only = TRUE)
YV3_crystal[[2]]
```

@@

```{r row_spacing.m}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(fungicide_ai, row_spacing, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   ggplot(aes(x = as.factor(row_spacing), y = Trials)) +
   xlab("Row Spacing (m)") +
   ylab("N Trials") +
   ggtitle(label = "Trial row spacing using tebuconazole") +
   geom_col(aes(fill = fungicide_ai),
            position = "dodge") +
   scale_fill_usq(name = "Fungicide AI") +
   theme_usq()

@@

```{r RS_yield}
# Which row spacing leads to the higher yeild potential
PM_MB_means %>%
   filter(year == 2017 |
             year == 2018) %>%
   #   filter(Fungicide == "control") %>%
   ggplot(aes(
      y = as.numeric(grain_yield.t.ha.),
      x = row_spacing,
      colour = location
   )) +
   geom_smooth(method = "gam") +
   geom_jitter(width = 0.01) +
   ggtitle("Grain yield results for different row spacing at three locations") +
   xlab("Row spacing (m)") +
   ylab("Grain yield - tonnes per hectare")
```

@@

### Season range and first incidence
Mungbean is a summer crop and powdery mildew requires cool conditions to establish.
Therefore the disease can be avoided by planting early in summer or spring, avoiding cooler temperatures at the end of some seasons.
Can we visualise when PM is most likely to establish over the calender year?

I'll build a plot of horizontal lines indicating the season length and use a dot on the line to indicating the day of the year first sign was observed for that trial.  
```{r first_incidence}
# Create the data frame for the plot
source("R/import_data.R")
PM_MB_means <- import_data()
season_dates <- PM_MB_means %>%
   group_by(trial_ref) %>%
   summarise(
      Planting_date = unique(planting_date),
      Harvest_date = unique(harvest_date),
      First_sign_PM = unique(first_sign_disease),
      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date))
   )

@@

first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273)+1
axis_labels_date <-
   c(
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[1], "%b-%d"),
      # Jan
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[2], "%b-%d"),
      # Feb
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[3], "%b-%d"),
      # March
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[4], "%b-%d"),
      # April
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[5], "%b-%d"),
      # May
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[6], "%b-%d"),
      # June
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[7], "%b-%d"),
      # July
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[8], "%b-%d"),
      # August
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[9], "%b-%d"),
      # Sept
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[10], "%b-%d") # October
   )

@@

# plot table as a box plot
PM_MB_means %>%
   filter(
      fungicide_ai == c(
         "200 g/L tebuconazole +\n120 g/L azoxystrobin" ,
         "200 g/L azoxystrobin +\n80 g/L cyproconazole",
         "tebuconazole",
         "propiconazole",
         "sulphur"
      )
   ) %>%
   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
   geom_boxplot() +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yield saved",
        title = "Grain yield proportion saved grouped by\nfungicide type") +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   guides(fill = guide_legend(title = "Fungicide")) +
   coord_flip()
```

>>>>

```{r Fungicide_x_nSprays_tble2, message=FALSE}
PM_MB_means %>%
   group_by(fungicide_ai, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   footnote(general = "Fungicides with less than five observations were omitted from this table")
```

@@

PM_MB_means %>%
   mutate(fungicide_ai = as.factor(PM_MB_means$fungicide_ai)) %>%
   filter(total_fungicide == 1 | total_fungicide == 2) %>%
   filter(
      fungicide_ai != "pyrazophos" &
         fungicide_ai != "control" &
         fungicide_ai != "benomyl" &
         fungicide_ai != "Acibenzolar-S-methyl"
   ) %>%
   mutate(fungicide_ai = factor(
      fungicide_ai,
      levels = c(
         "carbendazim",
         "pyraclostrobin",
         "sulphur",
         "200 g/L azoxystrobin +\n80 g/L cyproconazole",
         "tebuconazole",
         "propiconazole",
         "200 g/L tebuconazole +\n120 g/L azoxystrobin"
      )
   )) %>%
   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
   facet_grid(rows = vars(total_fungicide)) +
   geom_boxplot(aes(fill = fungicide_ai, alpha = 0.5)) +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   labs(y = "Proportion of grain yield saved",
        title = "Grain yield proportion saved\ngrouped by fungicide type") +
   theme(legend.position = "none") +
   scale_fill_usq() +
   coord_flip()
```

@@

#### Fungicide Doses  
We should check that all fungicide doses that were used were roughly the same if we are to compare between trials where dose might be different.

```{r tebuAndPropi_dose}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   select(
      trial_ref,
      year,
      location,
      first_sign_disease,
      fungicide_ai,
      dose_ai.ha,
      total_fungicide
   ) %>%
   ggplot(aes(x = as.factor(dose_ai.ha), fill = fungicide_ai)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Total number of treatments for each respective tebuconazole dose") +
   geom_bar() +
   scale_fill_usq() +
   scale_colour_usq()
```

@@

```{r PropiDoseEffect}
PM_MB_means %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = prop_YG)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Yield for each respective propiconazole dose") +
   geom_boxplot() +
   scale_fill_usq() +
   scale_colour_usq()
```

@@

```{r spray_relative2FS}
PM_MB_means %>%
   mutate(
      s1_DfromFS = fungicide_application_1 - first_sign_disease,
      s2_DfromFS = fungicide_application_2 - first_sign_disease,
      s3_DfromFS = fungicide_application_3 - first_sign_disease,
      s4_DfromFS = fungicide_application_4 - first_sign_disease,
      s5_DfromFS = fungicide_application_5 - first_sign_disease
   ) %>%
   gather(
      key = spray,
      value = n_days,
      s1_DfromFS,
      s2_DfromFS,
      s3_DfromFS,
      s4_DfromFS,
      s5_DfromFS
   ) %>%
   drop_na(n_days) %>% 
   ggplot(aes(x = spray, y = as.numeric(n_days))) +
   geom_violin() +
   scale_x_discrete(
      labels = c(
         "First\nspray",
         "Second\nspray",
         "Third\nspray",
         "Fourth\nspray",
         "Fifth\nspray"
      )
   ) +
   ylab("Days to First Sign of Disease")
```

@@

```{r Host_genotype}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(host_genotype, fungicide_ai, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   ggplot(aes(x = host_genotype, y = Treatments, fill = fungicide_ai)) +
   xlab("Cultivar") +
   ylab("N Trials") +
   ggtitle(label = "Cultivars used in either tebuconazole or propiconazole trials") +
   geom_col() +
   scale_fill_usq()
```

@@

YV1 <-
   yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
YV1[[2]] + 
   scale_fill_usq()

YV1[[3]]
```
Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray treatments.
```{r yieldVol_control}

YV2 <-
   yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
YV2[[2]] +
   scale_fill_usq()
YV2[[3]]
```

Volatility of the cultivars are fairly similar when trial is not considered as a factor (when we inspect plots of all treatments and only spray treatments). Green Diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials

@@

Let's examine the same plots as above but only for the most commonly used trial site, Hermitage.  
```{r yieldVol_Herm}
YV1_herm <-
   yield_volatility(
      genotype_by_trial = FALSE,
      control_only = FALSE,
      location = "Hermitage"
   )
YV1_herm[[2]] +
   scale_fill_usq()
```

@@

Let's take a closer look at Crystal with spray management treatments and without.  
```{r YieldVol_Crystal}
YV1_crystal <-
   yield_volatility(genotype = "Crystal", control_only = FALSE)
YV1_crystal[[2]] +
   scale_fill_usq()

YV1_crystal <-
   yield_volatility(genotype = "Crystal", control_only = TRUE)
YV1_crystal[[2]] +
   scale_fill_usq()
```

@@

Let's look at Jade, to see if it differs.
```{r YieldVol_Jade}
YV2_crystal <- yield_volatility("Jade",control_only = FALSE)
YV2_crystal[[2]] +
   scale_fill_usq()
```

@@

```{r YieldVol_JadeControl}
YV3_crystal <- yield_volatility("Jade", control_only = TRUE)
YV3_crystal[[2]] +
   scale_fill_usq()
```

@@

```{r row_spacing.m}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(fungicide_ai, row_spacing, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   ggplot(aes(x = as.factor(row_spacing), y = Trials)) +
   xlab("Row Spacing (m)") +
   ylab("N Trials") +
   ggtitle(label = "Trial row spacing using tebuconazole") +
   geom_col(aes(fill = fungicide_ai),
            position = "dodge") +
   scale_fill_usq(name = "Fungicide AI")

@@

```{r RS_yield}
# Which row spacing leads to the higher yield potential
PM_MB_means %>%
   filter(year == 2017 |
             year == 2018) %>%
   ggplot(aes(
      y = as.numeric(grain_yield.t.ha.),
      x = row_spacing,
      colour = location
   )) +
   geom_jitter(width = 0.01) +
   ggtitle("Grain yield results for different row spacing at three locations") +
   xlab("Row spacing (m)") +
   ylab("Grain yield - tonnes per hectare") +
   scale_colour_usq()
```

@@

### Season range and first incidence
Mungbean is a summer crop and powdery mildew requires cool conditions to establish.
Therefore the disease can be avoided by planting early in summer or spring, avoiding cooler temperatures at the end of some seasons.
Can we visualise when PM is most likely to establish over the calendar year?

I'll build a plot of horizontal lines indicating the season length and use a dot on the line to indicating the day of the year first sign was observed for that trial.

```{r first_incidence}
# Create the data frame for the plot
source("R/import_data.R")
PM_MB_means <- import_data()
season_dates <- PM_MB_means %>%
   group_by(trial_ref) %>%
   summarise(
      Planting_date = unique(planting_date),
      Harvest_date = unique(harvest_date),
      First_sign_PM = unique(first_sign_disease),
      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date))
   )

@@

first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273) + 1
axis_labels_date <-
   c(
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[1], "%b-%d"),
      # Jan
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[2], "%b-%d"),
      # Feb
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[3], "%b-%d"),
      # March
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[4], "%b-%d"),
      # April
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[5], "%b-%d"),
      # May
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[6], "%b-%d"),
      # June
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[7], "%b-%d"),
      # July
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[8], "%b-%d"),
      # August
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[9], "%b-%d"),
      # Sept
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[10], "%b-%d") # October
   )

@@

# plot table as a box plot
PM_MB_means %>%
   filter(
      fungicide_ai == c(
         "200 g/L tebuconazole +\n120 g/L azoxystrobin" ,
         "200 g/L azoxystrobin +\n80 g/L cyproconazole",
         "tebuconazole",
         "propiconazole",
         "sulphur"
      )
   ) %>%
   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
   geom_boxplot() +
   geom_hline(aes(yintercept = 0), size = 0.5, colour = "red") +
   labs(x = "Proportion of grain yield saved",
        title = "Grain yield proportion saved grouped by\nfungicide type") +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   guides(fill = guide_legend(title = "Fungicide")) +
   coord_flip()
```

### 2020-05-22 04_MetaAnalysis.Rmd
writing and editing
Clean up visualsation to use USQ colours and clean up code, etc.

      # Plot the imputed errors for each trial
      Vplot <-
         slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),] %>%
         ggplot(aes(y = grain_yield.t.ha, trial)) +
         #geom_point()+
         geom_pointrange(
            ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] -
               (1.95 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
            ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] +
               (1.95 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
            position = "jitter"
         ) +
         ylim(0.2, 1.5)

@@

```{r imputation_MSE}
for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref) {
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
      exp(rnorm(
         n = 1,
         mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
         sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
      ))
}
```

@@

```{r Metafor-analysis}
PM_mv_AI <- rma.mv(
   yi,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial),
   struct = "UN",
   data = slimmer_PM_dat
)

@@

@@

# results_AI <- data.frame(cbind(PM_mv_AI$b,
#                               (PM_mv_AI$ci.lb),
#                               PM_mv_AI$ci.ub))

@@

```{r Save_meta_data, eval=FALSE}
write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")

>>>>

      # Plot the imputed errors for each trial
      Vplot <-
         slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), ] %>%
         ggplot(aes(y = grain_yield.t.ha, trial)) +
         #geom_point()+
         geom_pointrange(
            ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] -
               (1.95 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
            ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] +
               (1.95 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
            position = "jitter"
         ) +
         ylim(0.2, 1.5)

@@

```{r imputation_MSE}
for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), ]$trial_ref) {
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
      exp(rnorm(
         n = 1,
         mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
         sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
      ))
}
```

@@

```{r Metafor-analysis}
PM_mv_AI <- rma.mv(
   yi,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial),
   struct = "UN",
   data = slimmer_PM_dat
)

@@

```{r Metafor-analysis}
PM_mv_AI <- rma.mv(
   yi,
   vi,
   mods = ~ slimmer_PM_dat$spray_management + slimmer_PM_dat$row_spacing + slimmer_PM_dat$host_genotype,
   method = "ML",
   random = list(~ spray_management | trial_ref),
   struct = "UN",
   data = slimmer_PM_dat
)

summary(PM_mv_AI)

@@

@@

```{r Save_meta_data, eval=FALSE}
write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
```
